\documentclass[10pt]{article}
\usepackage{ucsdcseletterhead}
\usepackage{parskip}
\usepackage[margin=1in]{geometry}
\usepackage{mathptmx}
\usepackage{courier}
\usepackage[scaled=.92]{helvet}
\usepackage[T1]{fontenc}
\pagestyle{empty}
\begin{document}
\hfill\today

Kim Barrett, Dean\\
Graduate Studies\\
402 University Center, 0003\\
UC San Diego\\
La Jolla, CA 92093-0003

\vskip\baselineskip
Dear Dean Barrett:

We request permission for Laura Smith to use the following publication
in her doctoral dissertation. Ms.\ Smith was the principle
researcher/author on this paper.

Smith, Laura; Smith, Jane D.; White, Sigmund. ``The Effect of Stress
Distribution on Photoelasticity,'' Name of Journal, vol. 4, 2011.

\vskip.5\baselineskip\centerline{$\sim$OR$\sim$}

We request permission for Laura Smith to use material that has been
submitted for publication. Ms. Smith was the principal
researcher/author on this paper.

Smith, Laura; Smith, Jane D.; White, Sigmund. ``The Effect of Stress
Distribution on Photoelasticity.''

\vskip.5\baselineskip\centerline{$\sim$OR$\sim$}

We request permission for Laura Smith to use material currently being
prepared for submission for publication. Ms. Smith was the principal
researcher/author on this paper.

Smith, Laura; Smith, Jane D.; White, Sigmund. ``The Effect of Stress
Distribution on Photoelasticity.''

\vskip3\baselineskip
\parbox[t]{.5\textwidth}{%
Professor Eta Theta\\
Chair of Committee}%
\parbox[t]{.5\textwidth}{%
Laura Smith}
\end{document}
